Working title: Ecological network control

### 2018-06-13 paper/manuscript.Rmd
Figure keystoness uses now model predictions

```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*0.5, fig.cap="unfinished figure"}
drake::loadd(fig_control_capacity)
fig_control_capacity[[1]] 
```

>>>>

```{r fig-species-level, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
drake::loadd(fig_control_capacity)
fig_control_capacity %>%
    cowplot::plot_grid(plotlist = .)
```
